---
title: "Practical Machine Learning Project"
author: "Jumadi"
date: "May 28, 2019"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Background

Using devices such as Jawbone Up, Nike FuelBand, and Fitbit it is now possible to collect a large amount of data about personal activity relatively inexpensively. These type of devices are part of the quantified self movement - a group of enthusiasts who take measurements about themselves regularly to improve their health, to find patterns in their behavior, or because they are tech geeks. One thing that people regularly do is quantify how much of a particular activity they do, but they rarely quantify how well they do it. In this project, your goal will be to use data from accelerometers on the belt, forearm, arm, and dumbell of 6 participants. They were asked to perform barbell lifts correctly and incorrectly in 5 different ways. More information is available from the website here: http://groupware.les.inf.puc-rio.br/har (see the section on the Weight Lifting Exercise Dataset).

### Load Library
```{r}
library(caret)
library(rattle)
```

### Load & Cleansing Data
```{r}
train_data <- read.csv('pml-training.csv',header=TRUE)
test_data <- read.csv('pml-testing.csv',header=TRUE)
```
```{r}
str(train_data)
```

```{r}
str(test_data)
```
Remove Variable with 80% NA/Blank Value
```{r}
index_col_train <- which(colSums(is.na(train_data) |train_data=="")>0.9*dim(train_data)[1]) 
train_clean <- train_data[,-index_col_train]
train_clean <- train_clean[,-c(1:7)]
dim(train_clean)
```

```{r}
index_col_train <- which(colSums(is.na(test_data) |test_data=="")>0.9*dim(test_data)[1]) 
test_clean <- test_data[,-index_col_train]
test_clean <- test_clean[,-c(1:7)]
dim(test_clean)
```

###Split data train to train & testing
For training data we split data training in 80% for training model dan 20% for testing model

```{r}
set.seed(33123)
inTrain1 <- createDataPartition(train_clean$classe, p=0.8, list=FALSE)
Train1 <- train_clean[inTrain1,]
Test1 <- train_clean[-inTrain1,]
dim(Train1)
```

## Modelling
for this data i'm using several algorithms to predict :
1. Decision trees
2. Random Forest
and using validation with cross validation

### Prediction with Decision Trees
```{r}
trctrl <- trainControl(method="cv", number = 5)
model_dt <- train(classe~., data=Train1, method="rpart", trControl=trctrl)
fancyRpartPlot(model_dt$finalModel)
```

#### validation
```{r}
pred_dt <- predict(model_dt, Test1)
confusionMatrix(pred_dt, Test1$classe)

```

from summary above the accuracy of this first model is very low (about 50%)

### Prediction with Random Forest

```{r}
model_RF <- train(classe~., data=Train1, method="rf", trControl=trctrl, verbose=FALSE)
print(model_RF)
```

```{r}
plot(model_RF,main="Accuracy of Random forest model by number of predictors")
```

#### validation
```{r}
pred_rf <- predict(model_RF, Test1)
confusionMatrix(pred_rf, Test1$classe)

```

```{r}
plot(model_RF$finalModel,main="Model error of Random forest model by number of trees")
```

from summary above the accuracy of this model is very hight (about 99%) with out of sample error  in 3%

### Conclussion
From summary 2 model above the highest accuracy is random forest model(about 99%). so we can use this model to pridict test case data

### Predict Result with testing data Using Random Forest

```{r}
FinalTestPred <- predict(model_RF,newdata=test_clean)
FinalTestPred
```

